
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
#knitr::opts_knit$set(root.dir=normalizePath('../'))
```


# Preliminary Setup and Data Import

Load libraries.  If you don't have any then you need to run, for example, install.packages("fmsb") in the console ONCE.  Don't include it in the code itself.
```{r load libraries}
library(httr)
library(tidyverse)
library(janitor)
library(broom)
library(tidyr)
library(fmsb) # contains ChronbachAlpha 
```

Get Data directly from OSF and then save it as a .rds file.  You need to run this chunk once since we're not updating or changing the excel spreadsheet. I but a `#` in front of it all to make this point.  As long as you have 'kayla.rds' in your folder then you're good to go. 
```{r import data, eval=FALSE, include=FALSE}
#if (!file.exists('kayla.xlsx')) {
#   data <- GET('osf.io/xnfg5//?action=download',
#                write_disk('kayla.xlsx'))#, overwrite = TRUE))
#}

# get data and clean
#kayla.tb <- readxl::read_excel('kayla.xlsx')
#kayla.tb <- kayla.tb %>%  
#  clean_names()
# saved it as an .rds
#saveRDS(kayla.tb, file = "kayla.rds")
```

Open the Saved Data.  You'll likely run this everytime as long as you close your R project.  Make sure you're working in your R project.  The top right shoudl have a blue cube that says "dissertation", if i'm remembering correctly.
```{r open data}
kayla_raw  <- read_rds("kayla.rds")
```


# Data Wrangling

Rename the SASB variables in the excel to match the SASB clusters.  
```{r rename sasb variables}
# we rename introject first
kayla_processed <- kayla_raw %>%
  rename(intcl1b = sasb_1, 
         intcl2b = sasb_6,
         intcl3b = sasb_3,
         intcl4b = sasb_4,
         intcl5b = sasb_8,
         intcl6b = sasb_5,
         intcl7b = sasb_2,
         intcl8b = sasb_7,
         intcl1w = sasb_ia1,
         intcl2w = sasb_ia6,
         intcl3w = sasb_ia3,
         intcl4w = sasb_ia4,
         intcl5w = sasb_ia8,
         intcl6w = sasb_ia5,
         intcl7w = sasb_ia2,
         intcl8w = sasb_ia7,
  
     # renaming friend first 16 for pre      
         sostcl1p = sasb_fp14,
         sostcl2p = sasb_fp1,
         sostcl3p = sasb_fp6,
         sostcl4p = sasb_fp13,
         sostcl5p = sasb_fp9,
         sostcl6p = sasb_fp3,
         sostcl7p = sasb_fp12,
         sostcl8p = sasb_fp4,
         sosicl1p = sasb_fp11,
         sosicl2p = sasb_fp8,
         sosicl3p = sasb_fp15,
         sosicl4p = sasb_fp5,
         sosicl5p = sasb_fp10,
         sosicl6p = sasb_fp7,
         sosicl7p = sasb_fp16,
         sosicl8p = sasb_fp2,
    # renaming friend second 16 for pre
         ssotcl1p = sasb_fp30,
         ssotcl2p = sasb_fp17,
         ssotcl3p = sasb_fp22,
         ssotcl4p = sasb_fp29,
         ssotcl5p = sasb_fp25,
         ssotcl6p = sasb_fp19,
         ssotcl7p = sasb_fp28,
         ssotcl8p = sasb_fp20,
         ssoicl1p = sasb_fp27,
         ssoicl2p = sasb_fp24,
         ssoicl3p = sasb_fp31,
         ssoicl4p = sasb_fp21,
         ssoicl5p = sasb_fp26,
         ssoicl6p = sasb_fp23,
         ssoicl7p = sasb_fp32,
         ssoicl8p = sasb_fp18,
    
    # below is for after.  notice how the first sixteen and second sixteen are the same as above EXCEPT for the 'p' is now an 'a' 
    
        sostcl1a = sasb_fa14,
         sostcl2a = sasb_fa1,
         sostcl3a = sasb_fa6,
         sostcl4a = sasb_fa13,
         sostcl5a = sasb_fa9,
         sostcl6a = sasb_fa3,
         sostcl7a = sasb_fa12,
         sostcl8a = sasb_fa4,
         sosicl1a = sasb_fa11,
         sosicl2a = sasb_fa8,
         sosicl3a = sasb_fa15,
         sosicl4a = sasb_fa5,
         sosicl5a = sasb_fa10,
         sosicl6a = sasb_fa7,
         sosicl7a = sasb_fa16,
         sosicl8a = sasb_fa2,
    # second sixten for after     
         ssotcl1a = sasb_fa30,
         ssotcl2a = sasb_fa17,
         ssotcl3a = sasb_fa22,
         ssotcl4a = sasb_fa29,
         ssotcl5a = sasb_fa25,
         ssotcl6a = sasb_fa19,
         ssotcl7a = sasb_fa28,
         ssotcl8a = sasb_fa20,
         ssoicl1a = sasb_fa27,
         ssoicl2a = sasb_fa24,
         ssoicl3a = sasb_fa31,
         ssoicl4a = sasb_fa21,
         ssoicl5a = sasb_fa26,
         ssoicl6a = sasb_fa23,
         ssoicl7a = sasb_fa32,
         ssoicl8a = sasb_fa18,
    
     # renaming parent first 16 for pre 
    
         psostcl1p = sasb_pp14,
         psostcl2p = sasb_pp1,
         psostcl3p = sasb_pp6,
         psostcl4p = sasb_pp13,
         psostcl5p = sasb_pp9,
         psostcl6p = sasb_pp3,
         psostcl7p = sasb_pp12,
         psostcl8p = sasb_pp4,
         psosicl1p = sasb_pp11,
         psosicl2p = sasb_pp8,
         psosicl3p = sasb_pp15,
         psosicl4p = sasb_pp5,
         psosicl5p = sasb_pp10,
         psosicl6p = sasb_pp7,
         psosicl7p = sasb_pp16,
         psosicl8p = sasb_pp2,
    # renaming parent second 16 for pre
         pssotcl1p = sasb_pp30,
         pssotcl2p = sasb_pp17,
         pssotcl3p = sasb_pp22,
         pssotcl4p = sasb_pp29,
         pssotcl5p = sasb_pp25,
         pssotcl6p = sasb_pp19,
         pssotcl7p = sasb_pp28,
         pssotcl8p = sasb_pp20,
         pssoicl1p = sasb_pp27,
         pssoicl2p = sasb_pp24,
         pssoicl3p = sasb_pp31,
         pssoicl4p = sasb_pp21,
         pssoicl5p = sasb_pp26,
         pssoicl6p = sasb_pp23,
         pssoicl7p = sasb_pp32,
         pssoicl8p = sasb_pp18,
    
    # renaming parent first 16 for after
    
         psostcl1a = sasb_pa14,
         psostcl2a = sasb_pa1,
         psostcl3a = sasb_pa6,
         psostcl4a = sasb_pa13,
         psostcl5a = sasb_pa9,
         psostcl6a = sasb_pa3,
         psostcl7a = sasb_pa12,
         psostcl8a = sasb_pa4,
         psosicl1a = sasb_pa11,
         psosicl2a = sasb_pa8,
         psosicl3a = sasb_pa15,
         psosicl4a = sasb_pa5,
         psosicl5a = sasb_pa10,
         psosicl6a = sasb_pa7,
         psosicl7a = sasb_pa16,
         psosicl8a = sasb_pa2,
    
# second parent sixteen for after     
         pssotcl1a = sasb_pa30,
         pssotcl2a = sasb_pa17,
         pssotcl3a = sasb_pa22,
         pssotcl4a = sasb_pa29,
         pssotcl5a = sasb_pa25,
         pssotcl6a = sasb_pa19,
         pssotcl7a = sasb_pa28,
         pssotcl8a = sasb_pa20,
         pssoicl1a = sasb_pa27,
         pssoicl2a = sasb_pa24,
         pssoicl3a = sasb_pa31,
         pssoicl4a = sasb_pa21,
         pssoicl5a = sasb_pa26,
         pssoicl6a = sasb_pa23,
         pssoicl7a = sasb_pa32,
         pssoicl8a = sasb_pa18)
```



The following creates weighted summary scores for SASB Affiliation and Autonomy by SASB surface.
```{r SASB weighted summary scores}
###### 1. Introject
int <-  kayla_processed %>%
  mutate(surf_1_1 = (intcl1b*0) + (intcl2b*4.5) + (intcl3b*7.8) + (intcl4b*4.5) + (intcl5b*0) + (intcl6b*-4.5) + (intcl7b*-7.8) + (intcl8b*-4.5),
         surf_2_1 = (intcl1b*7.8) + (intcl2b*4.5) + (intcl3b*0) + (intcl4b*-4.5) + (intcl5b*-7.8) + (intcl6b*-4.5) + (intcl7b*0) + (intcl8b*4.5),
         surf_1_2 = (intcl1w*0) + (intcl2w*4.5) + (intcl3w*7.8) + (intcl4w*4.5) + (intcl5w*0) + (intcl6w*-4.5) + (intcl7w*-7.8) + (intcl8w*-4.5),
         surf_2_2 = (intcl1w*7.8) + (intcl2w*4.5) + (intcl3w*0) + (intcl4w*-4.5) + (intcl5w*-7.8) + (intcl6w*-4.5) + (intcl7w*0) + (intcl8w*4.5)) %>%
  select(client_number, group, surf_1_1, surf_1_2, surf_2_1, surf_2_2)


# SOST/SOSI PRE
sosp <- kayla_processed %>%
  mutate(surf_3_1 = (sostcl1p*0) + (sostcl2p*4.5) + (sostcl3p*7.8) + (sostcl4p*4.5) + (sostcl5p*0) + (sostcl6p*-4.5) + (sostcl7p*-7.8) + (sostcl8p*-4.5),
         surf_4_1 = (sostcl1p*7.8) + (sostcl2p*4.5) + (sostcl3p*0) + (sostcl4p*-4.5) + (sostcl5p*-7.8) + (sostcl6p*-4.5) + (sostcl7p*0) + (sostcl8p*4.5),
         # significant other reacting to subjects - affiliation and pre and autonomy pre
         surf_5_1 = (sosicl1p*0) + (sosicl2p*4.5) + (sosicl3p*7.8) + (sosicl4p*4.5) + (sosicl5p*0) + (sosicl6p*-4.5) + (sosicl7p*-7.8) + (sosicl8p*-4.5),
         surf_6_1 = (sosicl1p*7.8) + (sosicl2p*4.5) + (sosicl3p*0) + (sosicl4p*-4.5) + (sosicl5p*-7.8) + (sosicl6p*-4.5) + (sosicl7p*0) + (sosicl8p*4.5)) %>%
  select(client_number, surf_3_1, surf_4_1, surf_5_1, surf_6_1)


# SSOT/SSOI PRE --------------------
ssop <- kayla_processed %>%
  mutate(surf_7_1 = (ssotcl1p*0) + (ssotcl2p*4.5) + (ssotcl3p*7.8) + (ssotcl4p*4.5) + (ssotcl5p*0) + (ssotcl6p*-4.5) + (ssotcl7p*-7.8) + (sostcl8p*-4.5),
         surf_8_1 = (ssotcl1p*7.8) + (ssotcl2p*4.5) + (ssotcl3p*0) + (ssotcl4p*-4.5) + (ssotcl5p*-7.8) + (ssotcl6p*-4.5) + (ssotcl7p*0) + (ssotcl8p*4.5),
         # subject reacting towards significant other - affiliation pre and autonomy pre
        surf_9_1 = (ssoicl1p*0) + (ssoicl2p*4.5) + (ssoicl3p*7.8) + (ssoicl4p*4.5) + (ssoicl5p*0) + (ssoicl6p*-4.5) + (ssoicl7p*-7.8) + (sostcl8p*-4.5),
         surf_10_1 = (ssoicl1p*7.8) + (ssoicl2p*4.5) + (ssoicl3p*0) + (ssoicl4p*-4.5) + (ssoicl5p*-7.8) + (ssoicl6p*-4.5) + (ssoicl7p*0) + (ssoicl8p*4.5)) %>%
  select(client_number, surf_7_1, surf_8_1, surf_9_1, surf_10_1)

# SOST-SOSI AFTER       
sosa <- kayla_processed %>%
  mutate(surf_3_2 = (sostcl1a*0) + (sostcl2a*4.5) + (sostcl3a*7.8) + (sostcl4a*4.5) + (sostcl5a*0) + (sostcl6a*-4.5) + (sostcl7a*-7.8) + (sostcl8a*-4.5),
         surf_4_2 = (sostcl1a*7.8) + (sostcl2a*4.5) + (sostcl3a*0) + (sostcl4a*-4.5) + (sostcl5a*-7.8) + (sostcl6a*-4.5) + (sostcl7a*0) + (sostcl8a*4.5),
         # significant other reacting to subjects - affiliation and after and autonomy after
         surf_5_2 = (sosicl1a*0) + (sosicl2a*4.5) + (sosicl3a*7.8) + (sosicl4a*4.5) + (sosicl5a*0) + (sosicl6a*-4.5) + (sosicl7a*-7.8) + (sosicl8a*-4.5),
         surf_6_2 = (sosicl1a*7.8) + (sosicl2a*4.5) + (sosicl3a*0) + (sosicl4a*-4.5) + (sosicl5a*-7.8) + (sosicl6a*-4.5) + (sosicl7a*0) + (sosicl8a*4.5)) %>%
  select(client_number, surf_3_2, surf_4_2, surf_5_2, surf_6_2)
         
# SSOT-SOSI AFTER
ssoa <- kayla_processed %>%
  mutate(surf_7_2 = (ssotcl1a*0) + (ssotcl2a*4.5) + (ssotcl3a*7.8) + (ssotcl4a*4.5) + (ssotcl5a*0) + (ssotcl6a*-4.5) + (ssotcl7a*-7.8) + (sostcl8a*-4.5),
         surf_8_2 = (ssotcl1a*7.8) + (ssotcl2a*4.5) + (ssotcl3a*0) + (ssotcl4a*-4.5) + (ssotcl5a*-7.8) + (ssotcl6a*-4.5) + (ssotcl7a*0) + (ssotcl8a*4.5),
         # subject reacting towards significant other - affiliation after and autonomy after
        surf_9_2 = (ssoicl1a*0) + (ssoicl2a*4.5) + (ssoicl3a*7.8) + (ssoicl4a*4.5) + (ssoicl5a*0) + (ssoicl6a*-4.5) + (ssoicl7a*-7.8) + (sostcl8a*-4.5),
         surf_10_2 = (ssoicl1a*7.8) + (ssoicl2a*4.5) + (ssoicl3a*0) + (ssoicl4a*-4.5) + (ssoicl5a*-7.8) + (ssoicl6a*-4.5) + (ssoicl7a*0) + (ssoicl8a*4.5)) %>%
  select(client_number, surf_7_2, surf_8_2, surf_9_2, surf_10_2)




### --------- Kalya - add parents here and follow the pattern above ----------- #####

# PSOST-PSOSI PRE

# PSSOT-PSSOI PRE

# PSOST-PSOSI After

# PSSOT-PSSOI After


```


```{r SASB weights Long Format}
# Create trimmed down coefficient table
coefficients <- bind_cols(int, sosp, ssop, sosa, ssoa) %>% 
  select(-client_number1, -client_number2, -client_number3, -client_number4)

# create long file to do multiple t-tests.
coefficents_long <- coefficients %>%
  gather(key, value, -client_number, -group) %>% 
  extract(key, c("surface", "state"), "(surf\\_.*)\\_(.)") %>%
  spread(state, value) %>%
  #clean_names() %>%
  rename(pre = `1`,
         post = `2`)

```


Summarize PANAS from Kayla
```{r panas subscales}
kayla_processed$panas1_1 <-  kayla_processed$panas_p1 + kayla_processed$panas_p3 + kayla_processed$panas_p5 + kayla_processed$panas_p9 + kayla_processed$panas_p10 + kayla_processed$panas_p12 + kayla_processed$panas_p14 + kayla_processed$panas_p16 + kayla_processed$panas_p17+ kayla_processed$panas_p19

kayla_processed$panas2_1 <-  kayla_processed$panas_p2+  kayla_processed$panas_p4+  kayla_processed$panas_p6+  kayla_processed$panas_p7+  kayla_processed$panas_p8+  kayla_processed$panas_p11+  kayla_processed$panas_p13+  kayla_processed$panas_p15+  kayla_processed$panas_p18+  kayla_processed$panas_p20
 
kayla_processed$panas1_2 <- kayla_processed$panas_a1 + kayla_processed$panas_a3 + kayla_processed$panas_a5 + kayla_processed$panas_a9 + kayla_processed$panas_a10 + kayla_processed$panas_a12 + kayla_processed$panas_a14 + kayla_processed$panas_a16 + kayla_processed$panas_a17 + kayla_processed$panas_a19
 
kayla_processed$panas2_2 <- kayla_processed$panas_a2+  kayla_processed$panas_a4+  kayla_processed$panas_a6+  kayla_processed$panas_a7+  kayla_processed$panas_a8+  kayla_processed$panas_a11+  kayla_processed$panas_a13+  kayla_processed$panas_a15+  kayla_processed$panas_a18+  kayla_processed$panas_a20
```

Calculate the Reliability for the PANAS.  You would need to install the package `fmsb`
```{r PANAS Reliability}
# Positive Affect Score - Prior
panaspospre.df <- kayla_tb[ , c("panas_p1", "panas_p3", "panas_p5", "panas_p9", "panas_p12", "panas_p14", "panas_p16", "panas_p17", "panas_p19")] 
CronbachAlpha(panaspospre.df) 
#.87

# Negative Affect Score Pior
panasnegpre.df <- kayla_tb[ , c("panas_p2", "panas_p4", "panas_p6", "panas_p7", "panas_p8", "panas_p11", "panas_p13", "panas_p15", "panas_p18", "panas_p20")] CronbachAlpha(panasnegpre.df) # doesn't work
#.87

# Positive Affect Score After
panasposafter.df <- kayla_tb[ , c("panas_a1", "panas_a3", "panas_a5", "panas_a9", "panas_a10", "panas_a12", "panas_a14", "panas_a16", "panas_a17", "panas_a19")] 
CronbachAlpha(panasposafter.df) # .80

## Negative Affect Score After
panasnegafter.df <- kayla_tb[ , c("panas_a2", "panas_a4", "panas_a6", "panas_a7", "panas_a8", "panas_a11", "panas_a13", "panas_a15", "panas_a18", "panas_a20")] 
CronbachAlpha(panasnegafter.df) # .87
```


### Add depressive versus stimulant category to data
```{r}

```





# Hypothesis Testing

## Hypothesis 1: Participants seeking treatment for substance abuse will report greater hoped-for affiliation in a reported significant-other relationship following use of their substance of choice compared to participants not seeking treatment for substance abuse. (Do not analyze drug of choice as stated in data analytic plan)

1a. Paired t-test and visualization for entire sample
```{r}
# 1. First, general paired t-tests for sostaff (sign other to subject transitive affiliation), ssotaff (subject to sign other transitive affiliation), sosiaff (sign other to subject intransitive affiliation), ssoiaff (subject to sign other intransitive affiliation)

coefficents_long %>%
       #arrange(time1) %>%
       group_by(surface, group) %>%
       do(tidy(t.test(.$pre, .$post, paired=TRUE)))  

```


1b. Residual change and differences by experimental (substance) and control (nonubstance) groups
###### SSOI AUT POST - Hypothesis 1 & 3



3. Calculate Residuals from SASB Data SOSIAUT, SSOIAFF, SSOIAUT
```{r SOSIAUT RES, }
# https://cran.r-project.org/web/packages/broom/vignettes/broom.html
dimensions <- kayla_processed %>%
  select(client_number, group, i_c, i_a, survey, gender, c(212:231))

coeff_model <- coefficents_long %>%
  nest(-surface) %>% 
  mutate(
    fit = map(data, ~ lm(post ~ pre, data = .x)),  # S3 list-col
    tidied = map(fit, tidy),
    glanced = map(fit, glance),
    augmented = map(fit, augment)
  )


coeff_model %>%
  unnest(glanced, .drop = TRUE)

coeff_model %>%
  unnest(augmented) %>% View()
  





fit1 <- lm(sostaffa ~ sostaffp, data = dimensions)

tidy(fit1)
#head(glance(fit))
resid1 <- augment(fit1)
resid.tb1 <- tbl_df(resid1)
resid.tb1 <- resid.tb1 %>% 
  select(.std.resid) %>%
  rename(sosiautzres = .std.resid)
```

```{r }
fit2 <- lm(sosiaffa ~ sosiaffp, data = dimensions)
#tidy(fit)
#head(glance(fit))
resid2 <- augment(fit2)
resid.tb2 <- tbl_df(resid2)
resid.tb2 <- resid.tb2 %>% 
  select(.std.resid) %>%
  rename(ssoiautzres = .std.resid)
`

```{r}

```



## Hypothesis 2: Adolescents who reported depressants (alcohol, marijuana, narcotics) as their drug of choice will rate their significant others as more sulking and resentful prior to using compared to adolescents who do not report depressants as their drug of choice. 
```{r}

```


## Hypothesis 3: Participants seeking treatment for substance abuse will report greater hoped-for introject (self-concept) affiliation following use of their substance of choice compared to participants not seeking treatment for substance abuse.
```{r}

```

## Hypothesis 4: Participants seeking treatment for substance abuse will report less negative affect following use of their substance of choice compared to participants not seeking treatment for substance abuse.
```{r}
kayla_processed
```


## Hypothesis 5: Participants not seeking treatment for substance abuse will report greater positive affect following substance use compared to participants seeking treatment for substance abuse.



```{r select panas data, echo=FALSE}
# Make a smaller version of data focused on PANAS
panas_data <- kayla_processed %>% select(client_number, group, panas1_1, panas1_2, panas2_1, panas2_2)
```

```{r calculate panas residuals, echo=FALSE}
# calculate positive residual change
panas1_fit <- lm(panas1_2 ~ panas1_1, data = panas_data)
resid1 <- augment(panas1_fit)
  
resid1_2 <- resid1 %>%
  select(.std.resid) %>%
  rename(panas1_res = .std.resid)

# calculate negative residual change
panas2_fit <- lm(panas2_2 ~ panas2_1, data = panas_data)
resid2 <- augment(panas2_fit)
  
resid2_2 <- resid2 %>%
  select(.std.resid) %>%
  rename(panas2_res = .std.resid)

#create a data file with residuals added 
panas_processed <- panas_data %>% bind_cols(resid1_2, resid2_2)
```

### Summary Statistics for PANAS

Mean and Standard Deviations by Group
```{r}
panas_data %>%
  group_by(group) %>%
  summarise(pos_pre_mean = mean(panas1_1),
            pos_post_mean = mean(panas1_2),
            neg_pre_mean = mean(panas2_1),
            neg_post_mean = mean(panas2_2),
            pos_pre_sd = sd(panas1_1),
            pos_pos_sd = sd(panas1_2),
            neg_pre_sd = sd(panas2_1),
            neg_post_sd = sd(panas2_2)) %>%
  knitr::kable()
```

Minimum and Maxiumum for PANAS Positive and Negative
```{r}
panas_data %>%
  group_by(group) %>%
  summarise(pos_pre_min = min(panas1_1),
            pos_pos_min = min(panas1_2),
            neg_pre_min = min(panas2_1),
            neg_post_min = min(panas2_2),
            pos_pre_max = max(panas1_1),
            pos_pos_max = max(panas1_2),
            neg_pre_max = max(panas2_1),
            neg_post_max = max(panas2_2)) %>%
  knitr::kable()
```


### Visualize PANAS Change


#### Distributions of PANAS

Empirical Cumulative Distribution Function for Positive (kayla, look this up for interpretation)
```{r}
panas_data %>%
  ggplot(aes(panas1_1, group=group)) +
  stat_ecdf(aes(color=group)) +
  ggtitle("ECDF for Positive at Pre")

panas_data %>%
  ggplot(aes(panas1_2, group=group)) +
  stat_ecdf(aes(color=group)) +
  ggtitle("ECDF for Positive at Post")
```
Interpret:

Empirical Cumulative Distribution Function for Negative (Kayla - you do this one)
```{r}
```
Interpret: 

#### PANAS Positive Change Overall
```{r}
panas_data %>% 
  gather(panas_positive, score, panas1_1, panas1_2, -client_number) %>%
  ggplot(aes(x=panas_positive, y=score, group=panas_positive)) +
  geom_boxplot() +
  geom_jitter(aes(color=panas_positive)) 
```

#### PANAS Positive Change by Group
```{r}
panas_data %>% 
  gather(panas_positive, score, panas1_1, panas1_2, -client_number) %>%
  ggplot(aes(x=panas_positive, y=score, group=panas_positive)) +
  geom_boxplot() +
  geom_jitter(aes(color=panas_positive)) +
  facet_wrap(~group)
```


#### PANAS Negative Affect Change
```{r}
panas_data %>% 
  gather(panas_negative, score, panas2_1, panas2_2, -client_number) %>%
  ggplot(aes(x=panas_negative, y=score, group=panas_negative)) +
  geom_boxplot() +
  geom_jitter(aes(color=panas_negative)) 
```

#### PANAS Negative Affect Change by Group
```{r}
panas_data %>% 
  gather(panas_negative, score, panas2_1, panas2_2, -client_number) %>%
  ggplot(aes(x=panas_negative, y=score, group=panas_negative)) +
  geom_boxplot() +
  geom_jitter(aes(color=panas_negative)) +
  facet_wrap(~group)
```

### Model PANAS Data

```{r}
positive_fit <- lm(panas1_res ~ group, data = panas_processed)
negative_fit <- lm(panas2_res ~ group, data = panas_processed)

arm::display(positive_fit)
arm::display(negative_fit)
```



```

## Hypothesis 6: Exploratory analyses will examine change in relationship and emotions associated with parental monitoring, peer acceptance, and diagnostic group.
```{r}

```



















